---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```

# qualiscapes

<!-- badges: start -->
[![R-CMD-check](https://github.com/ramongss/qualiscapes/workflows/R-CMD-check/badge.svg)](https://github.com/ramongss/qualiscapes/actions)
<!-- badges: end -->

The goal of `qualiscapes` is to get the preliminary 2019 QUALIS CAPES.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ramongss/qualiscapes")
```
## Example

Retrieve the data from the `get_qualis()` function, and show the head of the dataframe.

```{r echo=TRUE, message=FALSE, warning=FALSE}
da_qualis <- qualiscapes::get_qualis(file = NULL)

head(da_qualis)

```

Summarize the dataframe counting the number of journals/congresses according to the Qualis CAPES.

```{r echo=TRUE}
count_qualis <- 
  da_qualis %>% 
  dplyr::mutate(qualis = ESTRATO_2019) %>% 
  dplyr::group_by(qualis) %>% 
  dplyr::summarise(count = dplyr::n())

count_qualis
```

Plot the `count_qualis` dataframe to visualize the number of journals/congresses according to the preliminary 2019 Qualis CAPES.

```{r echo=TRUE}
count_qualis %>% 
  ggplot2::ggplot(ggplot2::aes(x = qualis, y = count)) +
  ggplot2::geom_col(ggplot2::aes(fill = qualis), colour = "black", show.legend = FALSE) +
  ggplot2::geom_text(ggplot2::aes(label = count), nudge_y = 300) +
  ggplot2::theme_bw() +
  ggplot2::labs(x = "Qualis CAPES", y = "No. of Journals/Congresses") +
  ggplot2::scale_color_discrete()
```

## Shiny App

https://ramongss.shinyapps.io/qualiscapes/
